---
title: "Column-wise operations: Your Turn"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(palmerpenguins)
```


## Your Turn #1

Take a look at the following code chunk:

```{r question-1-code, eval=FALSE, echo=TRUE}
penguins %>% 
  summarize(bill_length_mm = mean(bill_length_mm, na.rm = TRUE),
            bill_depth_mm = mean(bill_depth_mm, na.rm = TRUE))
```


```{r question-1}
question("Which of the following is equivalent to the code chunk shown above?",
  # wrong
  answer("`penguins %>% 
  summarize_if(vars(c(bill_length_mm, bill_depth_mm)), mean, na.rm = TRUE)`", 
  message = "Try again! The scoped verb you're looking for is `summarize_at()`"),
  # wrong
  answer("`penguins %>% 
  summarize_at(vars(c(bill_length_mm, bill_depth_mm)), mean)`",
  message = "Not quite. Don't forget about additional arguments to `mean()` that must be passed through with `...`"),
  # correct
  answer("`penguins %>% 
  summarize_at(vars(c(starts_with('bill'))), mean, na.rm = TRUE)`", correct = TRUE,
  message = "Nice work! You can use select helpers like `starts_with()` or `contains()` when selecting columns"),
  # wrong
  answer("`penguins %>% 
  summarize_at(c(bill_length_mm, bill_depth_mm), mean, na.rm = TRUE)`",
  message = "Not quite. Remember that the columns selected in `summarize_at()` must be wrapped inside `vars()`"),
   allow_retry = TRUE
)
```

## Your Turn # 2

### Faded example #1

Fill in the code blanks below to find the maximum value of all body dimensions (including body mass) for each combination of species and island using `dplyr::across()`. Specify a `.names` argument so that each output column name ends with the suffix `"_max"`.

```{r faded-example-1, exercise = TRUE, exercise.lines = 7}
penguins %>% 
  group_by(___, ___) %>% 
  summarize(___(c(where(___), -year), 
                   ___, na.rm = TRUE, 
                   .names = "___"))
```


```{r faded-example-1-solution}
penguins %>% 
  group_by(species, island) %>% 
  summarize(across(c(where(is.numeric), -year), 
                   max, na.rm = TRUE, 
                   .names = "{col}_max"))
```

### Faded example #2

Now perform the same calculation again, but this time specify the `.fns` argument using a named list and omit the `.names` argument. Be sure that your output columns have the same names as before (i.e. they still end with `"_max"`).

```{r faded-example-2, exercise=TRUE, exercise.lines = 6}

penguins %>% 
  group_by(___, ___) %>% 
  summarize(___(c(where(___), -year), 
                   ___(___ = ___), na.rm = TRUE))

```


```{r faded-example-2-solution}
penguins %>% 
  group_by(species, island) %>% 
  summarize(across(c(where(is.numeric), -year), 
                   list(max = max), na.rm = TRUE))
```
